\vspace{-0.25em}\thetitle

### 2009-07-23 paper.tex
...

@@

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traffic traces.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

Linear structure is clearly visible in \Figure{svd}:
the points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling near subspaces of more dimensions appear as ``smears.''

>>>>

\begin{figure*}[t]
\begin{center}
\subfloat[\footnotesize{DARTMOUTH}]{\includegraphics[width=1.15in]{svd/dart}}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.15in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.15in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2001}]{\includegraphics[width=1.15in]{svd/sc01}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.15in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.15in]{svd/ucsd}}
\caption{SVD flow-behavior scatter plots for the six network traffic traces considered in this paper.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure*}

A linear representation, as defined by Karpinski~\emph{et~al.}~\cite{Karpinski08}, maps sets of flows into a vector space such that union of sets becomes summation in the vector space:
\begin{align}
  \Phi(s_1 \union s_2) = \Phi(s_1) + \Phi(s_2).
\end{align}
The representation function, $\Phi$, should map each set of flows to a vector which in some sense describes their collective behavior.
For example: let $\Phi(s) \in \R^1$ be the number of packets in all the flows in as set $s$.
Since the number of total packets in the union of two sets of flows is the sum of the number in each individually, this representation is linear.

@@

Linear structure is clearly visible in \Figure{svd}:
the points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling near subspaces of more dimensions appear as ``smears.''
% There is a smattering of outliers, not especially near such structures.
